Thermodynamic response functions in a cell fluid model

### 2024-09-12 paper_text.tex

\begin{figure}[h!]
	\centering \includegraphics[width=0.5\textwidth]{f3a.pdf}
	\vskip-3mm\caption{The reduced thermal pressure coefficient $\beta^*_V$ as a function of the density $\rho^*$ at different values of relative temperature $\tau > 0$~($T > T_c$). Multiple isotherms collapsing onto the same line, making them indistinguishable at the scale of the figure.
	}\label{fig3a}
\end{figure}
\begin{figure}[h!]
	\centering \includegraphics[width=0.5\textwidth]{f3b.pdf}
	\vskip-3mm\caption{The reduced thermal pressure coefficient $\beta^*_V$ as a function of the effective chemical potential $M$ at different values of relative temperature $\tau > 0$~($T > T_c$). 
	}\label{fig3b}
\end{figure}
\begin{figure}[h!]
	\centering \includegraphics[width=0.5\textwidth]{f3c.pdf}
	\vskip-3mm\caption{The reduced thermal pressure coefficient $\beta^*_V$ as a function of the relative temperature $\tau$ at different values of the density $\rho^*$. 
	}\label{fig3c}
\end{figure}

>>>>

\begin{figure}[h!] 
	%\includegraphics[width=0.5\textwidth]{f3a.pdf}
	\includegraphics[width=\column]{f3a.pdf}
	\vskip-3mm
	\caption{The reduced thermal pressure coefficient $\beta^*_V$ as a function of the density $\rho^*$ at different values of relative temperature $\tau > 0$~($T > T_c$). Multiple isotherms collapsing onto the same line, making them indistinguishable at the scale of the figure.
	}
	\label{fig3a}
\end{figure}
\begin{figure}[h!]
	%\includegraphics[width=0.5\textwidth]{f3b.pdf}
	\includegraphics[width=\column]{f3b.pdf}
	\vskip-3mm
	\caption{The reduced thermal pressure coefficient $\beta^*_V$ as a function of the effective chemical potential $M$ at different values of relative temperature $\tau > 0$~($T > T_c$). 
	}
	\label{fig3b}
\end{figure}
\begin{figure}[h!]
	%\includegraphics[width=0.5\textwidth]{f3c.pdf}
	\includegraphics[width=\column]{f3c.pdf}
	\vskip-3mm
	\caption{The reduced thermal pressure coefficient $\beta^*_V$ as a function of the relative temperature $\tau$ at different values of the density $\rho^*$. 
	}
	\label{fig3c}
\end{figure}
